Data Preparation, Integration and Cleaning

### 2017-02-18 abbDataPrep_Script.Rmd
re-org of median rates, etc.

  str.data <- str.data[(str.data$max.date - str.data$min.date) >= 178, ]
  str.data <- str.data[str.data$max.date >= '2016-03-01' &
                         str.data$min.date <= '2016-03-01', ]
  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]

@@

@@

  str.data <- str.data[str.data$nightly.rate >= 50 &
                         str.data$nightly.rate <= 500, ]

@@

@@

### Median rate

  ## Remove those with less than 180 observed days (missing obs)
  str.data <- str.data[str.data$total.days >= 180, ]

>>>>

  str.data <- str.data[(str.data$max.date - str.data$min.date) >= 178, ]
  str.data <- str.data[str.data$max.date >= '2016-03-01' &
                         str.data$min.date <= '2016-03-01', ]

  daily.data <- daily.data[daily.data$date >= '2015-09-01', ]

@@

```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

  str.data <- str.data[str.data$nightly.rate >= 50 &
                         str.data$med.rate <= 500, ]

@@

#### Observed Revenue

Our final data filtering considers the observed revenue of the properties. For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.  In a number of extreme cases, time on market was extremely long and the total observed revenues very low. To remove these outlying observations, we filter out any properties with less than $5,000 in revenue.

For the short-term data, we first calculate the total number of bookings, the occupancy rate, blocked rate and proportion of the year over which the property was listed.  Using this data we sum up the total revenue from bookings. For properties that were not listed on the site for the entire year, we impute their annual revenue by dividing the actual revenue by the proportion of the year in which they were listed.^[Properties listed in summer, but not winter may be over imputed and vice versa, however, we expect the biases to cancel out over the entire sample.] Properties with no reserved bookings, and, therefore, no revenue, are removed.

Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.

```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}

  str.data$gross.revenue <- (str.data$bookings * str.data$med.rate) 
  ltr.data$gross.revenue <- ltr.data$event.price * (52 - ltr.data$dom / 7)

  str.small <- str.data[,c('baths', 'gross.revenue')]
  str.small$tenure <- 'short-term'
  ltr.small <- ltr.data[,c('baths', 'gross.revenue')]
  ltr.small$tenure <- 'long-term'
  all.small <- rbind(str.small, ltr.small)

  revdens <- ggplot(all.small, aes(x=gross.revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col)) +
    scale_color_manual(values=c(ltr.col, abb.col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
      bg='transparent')

    revdens

  save(revdens, file=paste0(fig.path, 'revdens.RData'))

  ltr.data <- ltr.data[ltr.data$gross.revenue > 10000, ]

@@
